Fig2

### 2020-03-26 analysis/figure-2.Rmd
new table 1, now with direction and control

candidategenes <- c("OXT", "AVP", "GNRH1", "GNRHR", "CGNRH-R",
                    "AR", "POMC", "AGRP", 
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2","VIP",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2","GRIA1",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16", 
                    "DIO3", "DIO2", "DIO1")

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "control_bldg") %>%
    arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
kable(table1)

>>>>

candidategenes <- c("OXT", "AVP", "GNRH1", "GNRHR", "CGNRH-R",
                    "AR",  "CYP19A1", 
                     "AVPR1A", "AVPR1B", "AVPR2","VIP",
                  "DRD1", "DRD2", 
                  "PRL", "PRLR",  
                    "ESR1","ESR2", "LBH",

                    "FOS", "JUN", "EGR1", "BDNF"
                      )

table1 <- allDEG %>%
  mutate(updown = ifelse(lfc > 0, "+", "-"))  %>%
  mutate(geneupdown = paste(gene, updown, sep = "")) %>%
  filter(gene %in% candidategenes) %>%
  arrange(geneupdown) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(geneupdown, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, control_bldg, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17, hatch_n5)  %>%
  arrange( tissue, sex)
kable(table1)
